Untitled

### 2025-01-20 Scripts/Test_for_danielle.Rmd
Code so Danielle can run the tuning sims

---
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r, prep-data,echo=F, message=F, warning=F, fig.width=6, fig.height=4,include=F,message=F}

if(load.results==F)
{
  Stocks <- ASR.long |> 
                      collapse::fsubset(!is.na(value)) |>
                      collapse::fgroup_by(Stock, type) |>
                      collapse::fsummarize(count=length(unique(value))) |>
                      collapse::fgroup_by(Stock) |>
                      collapse::fsummarize(types=length(unique(type))) |>
                      collapse::fsubset(types==5) |>
                      collapse::fselect(Stock)

  ASR.tmp <- ASR.long 
  ASR.tmp$age <- as.numeric(ASR.tmp$age)
  ASR.stocks <- ASR.tmp |> 
                          collapse::fsubset(Stock %in% Stocks$Stock) |>
                          collapse::fsubset(!is.na(value)) |>
                          collapse::roworder(Stock, Year, type, age)

  # print(Stocks)
  Stocks <- Stocks$Stock

  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
  # Esmarki doesn't work great as it is assessed using a quarterly model.
  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
  years.tmp <- NULL
  pnm.tmp <- NULL
  waa.tmp <- NULL
  ages.tmp <- NULL
  rem.tmp <- NULL
  mx.tmp <- NULL
  NE.tmp <- NULL
  vpa.tmp <- NULL
  am.tmp <- NULL
  #mr.tmp <- NULL
  abund.tmp <- NULL
  full.abund.tmp <- NULL
  full.rem.tmp <- NULL
  fs.tmp <- NULL
  for(i in Stocks)
  {
  print(i)
  ASR.sub <- ASR.long |>
    collapse::fselect(Year, Stock, type, age, value) |>
    collapse::fsubset(Stock==i)

    # Dropping the first 7 years as the 8 year olds are all missing
  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
  # 
  # # summary plots
  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
  #         theme_bw() + 
  #         ggtitle(i)
  # )

  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)

  data <- age.mat |>
    full_join(nat.mort) |>
    full_join(abund) |>
    full_join(weight.age) |>
    full_join(removals)

  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]

  # Tidy up the data for input...
  data$prop.nat.mort <- 1-exp(-data$NM)
  #prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))] <- 1-exp(-prop.nat.mort[,-which(names(prop.nat.mort) %in% c("Year", "Stock", "type"))])

  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)

  # Never run, so not doing anything.
  # missing_rem<- NULL
  # if(any(is.na(rem$rem))) 
  # {
  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
  # }

  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data |> dplyr::pull(Year) |> unique() |> sort()

  N.end <- sum(data[data$Year==max(years),]$Num)
  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- min(as.numeric(data$age))
  #maxage
  maxage <- max(as.numeric(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
  #tot.ssb
  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)

  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)

  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
  # So the R in 1970 were produced by SSB in 1969 when min age =0
  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
  # that gets us to the babies that show up in 1970
  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])

  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
                            collapse::fselect(-Year) |> as.data.frame()

  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
                 pivot_wider(names_from=age, values_from = mx) |> 
                 collapse::fselect(-Year) |> as.data.frame()
  # Get the abundance matrix
  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
                        pivot_wider(names_from=age, values_from = Num) |> 
                        collapse::fselect(-Year) |> as.data.frame()

  # Now we can save out the catch and get an instantaneous F
    data$Catch[is.na(data$Catch)] <- 0
    data$Exp <- data$Catch/data$Num 
    # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
    data$Exp[data$Exp == 1] <- 1.1
    # And make this an F
    data$Fs <- -log(1-data$Exp)
    if(any(is.na(data$Fs)))
    {
      fixers <- which(is.na(data$Fs))
      print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
      for(f in fixers)
      {
        yr <- data$Year[f]
        fs <- max(data$Fs[data$Year == yr],na.rm=T)
        data$Fs[f] <- fs
        data$Exp[f] <- 1-exp(-fs)
      }
    }

  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)

    if(i == "DFO_2J3KL_Gadus_morhua")
    {
      age.mat[,8:10] <- 1
      prop.nat.mort[,8:10] <- prop.nat.mort[,7]
      weight.age[12:14,9:10] <- weight.age[12:14,8]
      weight.age[15,10] <- weight.age[15,9]
      mx[12:16,9:10] <- mx[12:16,8]
      mx[17,10] <- mx[17,9]
      full.Fs[12:14,9:10] <- full.Fs[12:14,8]
      full.Fs[15,10] <- full.Fs[15,9]
      abund.age[12:14,9:10] <- abund.age[12:14,8]
      abund.age[15,10] <- abund.age[15,9]
      # I could calculate, but this will get us to the same place...
      full.rems[12:14,9:10] <- full.rems[12:14,8]
      full.rems[15,10] <- full.rems[15,9]
    }

    if(i == "DFO_4T-Spring_Clupea_harengus")
    {
      age.mat[6:7,10] <- 1
      prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
      weight.age[6:7,10] <- weight.age[6:7,9]
      mx[6:9,10] <- mx[6:9,9]
      full.Fs[6:7,10] <- full.Fs[6:7,9]
      abund.age[6:7,10] <- abund.age[6:7,9]
      full.rems[6:7,10] <- full.rems[6:7,9]
    }

    if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
    {
      age.mat[30,8] <- 1
      prop.nat.mort[30,8] <- prop.nat.mort[30,7]
      weight.age[30,8] <- weight.age[29,8]
      mx[30:31,8] <- mx[30:31,9]
      full.Fs[30,8] <- full.Fs[30,7]
      abund.age[30,8] <- abund.age[30,7]
      full.rems[30,8] <- full.rems[30,7]
    }

    if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
    {
      age.mat[c(14,27,40),5] <- age.mat[1,5]
      prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
      weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
      mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
      full.Fs[c(14,27,40),5] <- full.Fs[c(14,27,40),4]
      abund.age[c(14,27,40),5] <- abund.age[c(14,27,40),4]
      full.rems[c(14,27,40),5] <- full.rems[c(14,27,40),4]
    }
    # Clear out some 0's...
    if( i == "AFSC_EEBSAI_Limanda_aspera")
    {
      mx[5,18] <- mean(unlist(mx[5,c(17,19)]))
      mx[c(6,8),19] <- mx[c(6,8),18]
      mx[2:7,20] <- mx[2:7,19] 
    }

  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...

   if(minage >0) 
  {
    rm <- -(1:minage)
    years <- years[rm]
    prop.nat.mort <- prop.nat.mort[rm,]
    weight.age <- weight.age[rm,]
    rem <- rem[rm,]
    mx <- mx[rm,]
    vpa.abund <- vpa.abund[rm]
    age.mat <- age.mat[rm,]
    abund.age <- abund.age[rm,]
    full.Fs <- full.Fs[rm,]
    full.rems <- full.rems[rm,]
   }
  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
  #   names(mx) <- names(mx.fill)
  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  # }

    years.tmp[[i]] <- years
    pnm.tmp[[i]] <- prop.nat.mort
    waa.tmp[[i]] <- weight.age
    ages.tmp[[i]] <- minage:maxage
    rem.tmp[[i]] <- rem
    mx.tmp[[i]] <- mx
    NE.tmp[[i]] <- N.end
    vpa.tmp[[i]] <- vpa.abund
    am.tmp[[i]] <- age.mat
    #mr.tmp[[i]] <- missing_rem
    abund.tmp[[i]] <- abund.age
    fs.tmp[[i]] <- full.Fs
    full.rem.tmp[[i]] <- full.rems
  } #end input data loop

  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,#mr.tmp,
       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))

  } # end load results
```

@@

  if(load.results==F)
  {
  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))

  for.tune.all.res <- NULL
  for.tune.summary <- NULL
  for(i in Stocks)
  {
    years <- years.tmp[[i]]
    prop.nat.mort <- pnm.tmp[[i]] 
    #rem <- rem.tmp[[i]] 
    mx <- mx.tmp[[i]] 
    N.end <- NE.tmp[[i]] 
    ages <- ages.tmp[[i]]
    vpa.abund <- vpa.tmp[[i]] 
    abund <- abund.tmp[[i]]
    fs <-fs.tmp[[i]]
    full.rem <- full.rem.tmp[[i]]
    #full.abund <- full.abund.tmp[[i]]
    #all.abund <- full.abund.tmp[[i]]
    #N.end <- vpa.abund[length(vpa.abund)]
    #Pick your step size
    ss.size <- 0.005
    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
                            "DFO_2J3KL_Gadus_morhua",
                            "DFO_3Pn-4RS_Gadus_morhua",
                            "DFO_4T-4VN_Gadus_morhua",
                            "DFO_4T_Scomber_scombrus",
                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
                            "ICES-AFWG_NEA1-2_Gadus_morhua",
                            "ICES-HAWG_NS_Ammodytes_dubius",
                            "ICES-NWWG_FA5b_Pollachius_virens",
                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                            "ICES-WGCSE_IS7a_Gadus_morhua",
                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
                            "NEFSC_NWA_Scomber _scombrus")

@@

     for.tune.all.res[[i]] <- fast.for.tune
     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
     for.tune.summary[[i]] <- for.tune.tmp
  }

  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))
  # 
}# end if load results

@@

>>>>

---
title: "Untitled"
author: "David Keith"
date: "2025-01-20"
output: html_document
---

```{r load-libraries-n-data, echo = FALSE, cache = FALSE, message = FALSE, results = 'hide', warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# add other packages here:
library(dplyr)
library(readr)
library(tibble)
library(csasdown)
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
library(gtable)
library(viridis)
library(arm)
library(mgcv)
library(lme4)
library(scales)
library(ggh4x)
library(gratia)
theme_set(theme_few(base_size = 14))

# The location of your data
loc <- 'D:/GitHub/ICM'
# The parameters for the doubling time simulation
n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
n.sim.years <- 100
# If we already have the results don't re-run the models or load data we don't need.
# Note that running the models takes like 4 days to finish!!
load.results <- T
# What tunning model are you running or did you run!
what.2.tune <- 'fec_nm'

#source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))

# Download the functions we'll need from github
funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple_Lotka_r.r",
          #"https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
          #"https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r",
          "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/tuning_sim_fast.r"
)
  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
for(fun in funs) 
{
  download.file(fun,destfile = basename(fun))
  source(paste0(getwd(),"/",basename(fun)))
  file.remove(paste0(getwd(),"/",basename(fun)))
}

@@

  load(file = paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))

  for.tune.all.res <- NULL
  for.tune.summary <- NULL
  # Danielle this should run the code for Stock #2
  i <- Stocks[2] 
  #for(i in Stocks)
  #{
    years <- years.tmp[[i]]
    prop.nat.mort <- pnm.tmp[[i]] 
    #rem <- rem.tmp[[i]] 
    mx <- mx.tmp[[i]] 
    N.end <- NE.tmp[[i]] 
    ages <- ages.tmp[[i]]
    vpa.abund <- vpa.tmp[[i]] 
    abund <- abund.tmp[[i]]
    fs <-fs.tmp[[i]]
    full.rem <- full.rem.tmp[[i]]
    #full.abund <- full.abund.tmp[[i]]
    #all.abund <- full.abund.tmp[[i]]
    #N.end <- vpa.abund[length(vpa.abund)]
    #Pick your step size
    ss.size <- 0.005
    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
                            "DFO_2J3KL_Gadus_morhua",
                            "DFO_3Pn-4RS_Gadus_morhua",
                            "DFO_4T-4VN_Gadus_morhua",
                            "DFO_4T_Scomber_scombrus",
                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
                            "ICES-AFWG_NEA1-2_Gadus_morhua",
                            "ICES-HAWG_NS_Ammodytes_dubius",
                            "ICES-NWWG_FA5b_Pollachius_virens",
                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                            "ICES-WGCSE_IS7a_Gadus_morhua",
                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
                            "NEFSC_NWA_Scomber _scombrus")

@@

     for.tune.all.res[[i]] <- fast.for.tune
     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
     for.tune.summary[[i]] <- for.tune.tmp
  #}

}# end if load results

@@

STOP HERE DANIELLE, THE REST OF THIS STUFF IS JUST TAKING MODEL OUTPUT AND PLOTING OR MAKING SECONDARY PRODUCTS FROM THE RESULTS.
